Use and acquisition of causal relations for decision making under uncertainty using imperfect information games

### 2018-09-02 Propuesta/Formato/Proposal_format.tex
correcciones

	A causal graphical model (CGM) consists of a set of random variables $\mathcal{X}=\{ X_1,...,X_n \}$, an acyclic directed graph (DAG) whose nodes are in correspondence with the variables in $\mathcal{X}$ and whose edges represent relations of cause-effect. Also, the model, which up to this point is nothing more than a Bayesian Network with causal semantics, is enriched with an operator named $do()$ which is defined over graphs and whose action is described as follows: given $\mathbf{X} \subseteq \mathcal{X}$ and $\mathbf{x} = \{ x_{i_1}, x_{i_2}, ... , x_{i_j} \} \in Val(\mathcal{X})$ the action $do(\mathbf{X} = \mathbf{x} )$ corresponds to assign to each $X_j \in \mathbf{X}$ the value $x_{x_{i_j}}$ and to delete every incoming edges into the node corresponding to each $X_j$ in the graph $\mathcal{G}$ (\cite{koller2009probabilistic}, \cite{sucar2015probabilistic}) To apply the $do()$ operator over a variable (or set of variables) is also called as an \textit{intervention} over the variable. It is this interventional operator which separates associative models from causal models, since it provides the solution of the “probability raising” attempts to define causality, since if $X$ is a cause for $Y$ then $P(Y | do(X)) > P(Y)$ (\cite{pearl2018why}).

@@

	\subsection{Research Question}
How a rational decision maker who faces an uncertain environment which is governed by a causal mechanism can learn and make use of this causal structure in order to make good choices? How can a causal structure help a decision maker in order to guide his learning process? What does the rationality assumption implies about how to choose when considering causal information? How to trade off exploration and exploitation when trying to learn about the causal structure of an environment while also trying to make good choices?
	\subsection{Hypothesis}
	Let $\mathcal{G}$ a causal graphical model and let $(\mathcal{A},\mathcal{E},\mathcal{C})$ a decision problem whose actions $a_i = \{ c_j | E_j : j \in J \}$  are causally related to consequences $c \in \mathcal{C}$ through the uncertain events $E \in \mathcal{E}$ which correspond to variables in $\mathcal{G}$. Then, if a decision maker doesn't know the probabilities of the uncertain events in $E$, by repeatedly making decisions he can learn a causal model of the environment and use it to find the optimal action (in the sense of expected utility theory) in less, or equal, rounds than if he doesn't consider causal information.
	\subsection{Objectives}
		\subsubsection{General Objectives}
			The proposed research has as a general objective to understand what are the implications of causality for rational decision maker who faces an uncertain environment and how causal relations can be discovered and used in order to make good choices that maximize the expected utility for the decision maker.
		\subsubsection{Specific Objectives}
		\begin{enumerate}
		\item In order to achieve the general objective, we need to separate it into smaller problems which are required to be solved first. In first place, it is required to find a general way of defining a game that captures the interaction between a decision maker and a causal-governed environment.

@@

Reinforcement Learning can be roughly divided into two categories: model-based and model-free methods. In the former case the agent learns an \textit{optimal policy} from a model of the environment, such as the Dynamic Programming method explained in \cite{sutton1998reinforcement}. On the other hand, if the agent does not know the transition function, then he must learn directly values of \textit{state-action} pairs. A very well known model-free method is the classic Q-learning algorithm developed by \cite{watkins1992q}. In either case, model-free or model-based methods an agent must use information from transitions or from observations. For this reason, Reinforcement Learning uses only associative patterns for finding an optimal policy and this methods can not learn beyond what is expressable by an MDP, which is constrained into associative rules and can not express any other kind of structure, such as causal relations.

@@

The formation and use of causal knowledge in human beings can provide inspiration for our problem, and it has been extensively studied by York Hagmayer and his team They have found that human beings, while facing a sequential decision problem, use and modify causal information (\cite{hagmayer2008causal}, \cite{hagmayer2009decision}, \cite{hagmayer2010spontaneous}, \cite{hagmayer2013repeated}). In their studies, all of the subjects were faced with a one-stage decision problem in which an initial causal model was provided. In several rounds, the subject made a decision and observed a feedback and was later asked to describe the causal model they thought controlled the situation. The subjects knew that they were supposed to learn a causal model, but the case where the final objective is other than directly learning a causal model has not been studied. \cite{bramley2015conservative} show that people acquire causal structures by selecting the \textit{most informative} options, in the sense of decreasing uncertainty about the true model instead of maximizing expected utility.

@@

In the class of decision problems considered for this proposal it is assumed that the a rational agent must choose some available action and then receive a reward from it. In the case where the agent does not has enough information available, we consider a certain number of learning rounds and expect the agent to output a good action. Problems of this nature have been modelled as \textit{bandit} problems (\cite{sutton1998reinforcement}). A bandit is an analogy of a \textit{slot machine} as the ones found in Las Vegas, where a lever is pulled an some monetary reward (probably cero) is observed. A bandit problem consists by a set of available actions (the arms of the slot machine) and a reward function. It has been shown that the probability of the action selected in the $n$-th round not being optimal has an upper bound (\cite{audibert2010best}) if the optimality criteria is choosen to be the \textit{minimal regret} which is basically the difference of the theoretical mean reward of the optimal action and the chosen action. On the other hand, if the largest mean reward is desired with a fixed confidence of $\delta$ then an algorithm for finding the optimal action exist in such a way that the number of rounds to find it is within a constant factor of a lower bound (\cite{jamieson2014lil}).  If one does not consider a fixed confidence but instead a fixed number of learning rounds (known as fixed budget), then we face a \textit{fixed budget} problem where a lower bound for the probability of finding the optimal arm is given by \cite{carpentier2016tight}.

Notice that none of the previous works consider any kind of causal structure. For this kind of problems, causal relations between actions and consequences could be considered, in this way an action could be conceived as an \textit{intervention} over some environment, which is in fact how humans consider actions in the world (\cite{hagmayer2009decision}) and that human beings use and modify causal knowledge during a sequential decision making process (\cite{hagmayer2013repeated}). Consider a set of variables that are causally related between them and to a \textit{reward} variable whose value has to be maximized by intervening one of the variables. It is shown by \cite{lattimoreNIPS2016} that adding causal information in a fixed budget decision problem allows the decision maker to learn \textit{faster} had he not considered causal information. Their work requires that the causal model is fully known to the decision maker, this requirement is relaxed later by \cite{sen2017identifying} who requires only that some part of the causal model is known and allow interventions over the unknown part.

In \cite{lattimoreNIPS2016} a causal graphical model $\mathcal{G}$ is assumed to be known and a number of learning rounds $T$ is fixed. In round $t \in [1,...,T]$ the decision maker chooses $a_t=do(X_t = x_t)$ and observes a reward $Y_t$. After the $T$ learning rounds, the decision maker is expected to choose an optimal action $a^\ast$ that minimizes the \textit{expected regret}, which is defined as $R_T= \mu^\ast - \mathbb{E}[\mu_{a^\ast}]$ where $\mu^\ast = \max \mathbb{E}[a]$. They show that the achieved regret is of a smaller order than the regret obtained by non-causal algorithms.

Discovering the causal model itself while using current knowledge to make choices is left as future work in both \cite{lattimoreNIPS2016} and \cite{sen2017identifying}, but algorithms to discover causal relations in data can be found in \cite{eberhardt2008almost}, \cite{hauser2012two}, \cite{hyttinen2013experiment}, \cite{loh2014high}, \cite{shanmugam2015learning} \cite{mooij2016distinguishing}. Also, an \textit{active learning} approach can be used to learn causal models from data, where one starts with some initial graph and then select the instances in the data that allow to add and orient edges in order to end with a fully oriented graph. Active learning algorithms for causal discovery can be found in \cite{tong2001active},\cite{murphy2001active}, \cite{meganck2006learning}, \cite{he2008active}, \cite{hauser2012two}, \cite{10.1007/978-3-319-56970-3_9}, \cite{rubenstein2017probabilistic}.

@@

\newpage
\section{Methodology}
In this section we describe the steps that are to be followed in order to answer the Hypothesis.
\subsection{A guiding principle for a Causal Decision Problem}
We propose the following principle as a normative guide for how causal information must be used in order to find a solution to a decision problem where the preferences of the decision maker are assumed to be rational. We consider only the case where the decision maker's utility is given by the outcome of a $\{0,1 \}$-binary variable.
\begin{prop}
Let  $\mathcal{G}$ a causal graphical model and let $(\mathcal{A},\mathcal{E},\mathcal{C})$ a decision problem under uncertainty whose actions $a_i = \{ c_j | E_j : j \in J \}$  are causally related to consequences $c \in \mathcal{C}$ through the uncertain events $E \in \mathcal{E}$ which correspond to variables in $\mathcal{G}$. Let $Y$ a variable in $\mathcal{G}$ the variable whose realizations correspond to the consequences of the decision problem once the agent has chosen an action $a \in \mathcal{A}$ and assume that $Y$ only takes values in the set $\{ 0,1\}$ where $1$ is a more desired outcome for the agent. Then, the $\textit{solution}$ for this decision problem is given by the action $a^\ast \in \mathcal{A}$ that satisfies:
\[ P(Y=1 | do(a^\ast) \geq P(Y=1 | do(a)) \textrm{ for all } a \in \mathcal{A}. \]
\end{prop}
\subsection{Modelling a Decision Problem under Uncertainty as a Game}
Consider a decision problem under uncertainty $(\mathcal{A},\mathcal{E},\mathcal{C},\succeq)$ where the available actions $\mathcal{A}$ to a decision maker are causally related to the outcomes $\mathcal{C}$ and this causal relations are captured by a Causal Graphical Model $\mathcal{G}$. The Causal model is assumed to remain fixed and unknown to the decision maker, who is assumed to be rational and aware of the causal nature of the decision problem he faces.

@@

\subsection{Belief Formation}
Once a Game that models agent-environment interaction is defined, we must turn to the question about \textit{learning} about the environment, which includes acquiring causal information and also using current causal knowledge in order to obtain new information.

For the agent to learn and reason about the plays of Nature we assume that he is able to observe the final outcome of the game, which includes knowing about the inicial uncertain state that Nature assigned. The agent, at the beginning of the game is uncertain about the state of the environment which he is facing, but he still must take an action, so in order to allow the decision maker to use his knowledge to act, he will have \textit{beliefs} about any relevant aspects of the environment which he will use as if they were the true model in any given play. These beliefs will be \textit{updated} according to what is observed at the end of each game. The second step is to find a way to specify beliefs about causal structure.

@@

The three cases that we notice are:
\begin{itemize}
\item The decision maker knows the causal model.
\item The decision maker knows only the graphical \textit{structure} of the causal model.
\item The decision maker knows nothing about the causal model. 
\end{itemize}
In the following we show how the first two cases, which are particular cases of our general problem, can be solved and we show that the proposed solution for the first two cases sheds light on how the general case could be solved.
\subsubsection{Fully knowing the causal graphical model}
If the decision maker knows the causal graphical model, then following the guiding principle, he could easily calculate the effect on the target variable that any of his actions has and then choose the action that has the highest probability of causing a \textit{desired} value of the target variable. The decision thus made is the one that maximizes the expected utility, by construction. Also, choosing this action is the \textit{best response} action, and therefore a Nash equilibrium for the game. Choosing the action that is more likely to produce the most desired outcome according to current causal knowledge is required by Joyce's Causal Decision Theory (\cite{joyce1999foundations}).
\subsubsection{Knowing only the graph structure}
If a decision maker knows the structure of the graph, but he does not know the parameters, then he encodes this ignorance, along with any useful previous knowledge, as a probability distribution over a suitable space. In the preliminary results that will be shown later a particular case is considered, where the beliefs have the form of a Dirichlet distribution for each of the Conditional Probability Tables that characterize a Bayesian Network.

In general, what must be specified is a way of encoding current causal knowledge into a probability distribution in such a way that a \textit{local} (i.e. in each round) causal model can be obtained from current beliefs in order to make a decision using current causal knowledge and those beliefs will be later updated using what is observed after choosing an action.  The action will be chosen, given a set of beliefs, as in the previous case and by following the guiding principle. This means that using current beliefs, the agent forms a causal model which is used as if it were the true causal model.
\subsubsection{General case: Model unknown}
The previous two cases are per se steps of the methodology, rather simplifications in order to understand what is happening. The real deal is the case where the causal model is unknown.

When the causal model is unknown, two cases of interest appear, depending if the decision maker knows the (maximum) number of variables in the model or not.

@@

Given a number $T$ of rounds, and inside round $t \in \{1,2,...,T \}$ the agent will make an action $a \in \mathcal{A}$ and then observe the state of the other variables of the model. Using this information, current beliefs will be updated according to the criteria to be established.

@@

\end{itemize}
\subsubsection{Publications plan}
\begin{itemize}
\item \textbf{Year 1:} Gonzalez-Soto, M., Sucar, L.E., Escalante, H.J., \textbf{Playing against Nature: causal discovery for decision making under uncertainty}. Accepted for poster presentation at the \textbf{CausalML 2018 Workshop at ICML 2018}. July 15 2018, Stockholm, Sweden. This can be confirmed at \url{https://sites.google.com/site/faim18wscausalml/program-schedule}. The paper can be found at \url{https://arxiv.org/abs/1807.01268}.
\item \textbf{Year 2:} Conference Paper
		\begin{itemize}
		\item The implications of Causal Relations for Decision Making: a general principle for Decision under Uncertainty.
		\end{itemize}
\item \textbf{Year 2:} Conference Paper
	\begin{itemize}
	\item When a causal model is unknown, how to encode uncertainties about causal structure in a probabilistic distribution? Bayesian Nonparametric prior that explicitly represents causal structure.
	\end{itemize}
\item \textbf{Year 3:} Journal Paper
		\begin{itemize}
			\item Aim: Theoretical paper of results for on-line causal learning.
		\end{itemize}
\end{itemize}

@@

\[ f(x_1,...,x_k | \alpha_i,...,\alpha_k)=\frac{1}{B(\alpha)}  \prod_{i=1}^k x_i^{\alpha_i-1},\]

@@

\subsubsection{Implementation}
We begin with a random assignation of the $\alpha$ parameter for each of the distributions considered. We use Dirichlet distribution for each of the conditional probability tables that appear in the factorization of the joint probability for the graph of $\mathcal{G}$. Since each of the variables in the model is binary, then the product of these Dirichlets is Dirichlet.

@@

The average perform over $20, 50, 100$ and $200$ rounds are shown.

>>>>

	A causal graphical model (CGM) consists of a set of random variables $\mathcal{X}=\{ X_1,...,X_n \}$, an acyclic directed graph (DAG) whose nodes are in correspondence with the variables in $\mathcal{X}$ and whose edges represent relations of cause-effect. Also, the model, which up to this point is nothing more than a Bayesian Network with causal semantics, is enriched with an operator named $do()$ which is defined over graphs and whose action is described as follows: given $\mathbf{X} \subseteq \mathcal{X}$ and $\mathbf{x} = \{ x_{i_1}, x_{i_2}, ... , x_{i_j} \} \in Val(\mathcal{X})$ the action $do(\mathbf{X} = \mathbf{x} )$ corresponds to assign to each $X_j \in \mathbf{X}$ the value $x_{x_{i_j}}$ and to delete every incoming edges into the node corresponding to each $X_j$ in the graph $\mathcal{G}$ (\cite{koller2009probabilistic}, \cite{sucar2015probabilistic}). To apply the $do()$ operator over a variable (or set of variables) is also called as an \textit{intervention} over the variable. It is this interventional operator which separates associative models from causal models, since it provides the solution of the “probability raising” attempts to define causality, since if $X$ is a cause for $Y$ then $P(Y | do(X)) > P(Y)$ (\cite{pearl2018why}). In fact, using the \textit{Do} operator we give a definition of a variable $X$ causing $Y$.
	Let $\mathcal{G}$ a Causal Graphical Model and $P_\mathcal{G}$ its corresponding distribution and let $X$ and $Y$ variables in the model. We say that $X$ \textit{causes} $Y$ if 
	\[ P_\mathcal{G}(Y | do(X=x) \neq P_\mathcal{G}(Y | do(X=x'). \]

@@

	\subsection{Research Question}
The proposed research is ultimately trying to answer a series of questions about the nature of causal relations and about their possible use.
\begin{enumerate}
\item How a rational decision maker who faces an uncertain environment which is governed by a causal mechanism can learn and make use of this causal structure in order to make good choices? \item How can a causal structure help a decision maker in order to guide his learning process? 
\item What does the rationality assumption implies about how to choose when considering causal information? 
\item How to trade off exploration and exploitation when trying to learn about the causal structure of an environment while also trying to make good choices?
\end{enumerate}
	\subsection{Hypothesis}
	Let $\mathcal{G}$ a causal graphical model and let $(\mathcal{A},\mathcal{E},\mathcal{C})$ a decision problem whose actions $a_i = \{ c_j | E_j : j \in J \}$  are causally related to consequences $c \in \mathcal{C}$ through the uncertain events $E \in \mathcal{E}$ which correspond to variables in $\mathcal{G}$. Then, if a decision maker doesn't know the probabilities of the uncertain events in $E$, by repeatedly making decisions he can learn a causal model of the environment and use it to find the optimal action (in the sense of expected utility theory) in less, or equal, rounds than if he doesn't consider causal information.
	\subsection{Objectives}
		\subsubsection{General Objectives}
			The proposed research has as a general objective to understand what are the implications of causality for rational decision maker who faces an uncertain environment and how causal relations can be discovered and used in order to make good choices that maximize the expected utility for the decision maker.
		\subsubsection{Specific Objectives}
		\begin{enumerate}
		\item In order to achieve the general objective, we need to separate it into smaller problems which are required to be solved first. In first place, it is required to find a general way of defining a game that captures the interaction between a decision maker and a causal-governed environment.

@@

Reinforcement Learning can be roughly divided into two categories: model-based and model-free methods. In the former case the agent learns an \textit{optimal policy} from a model of the environment, such as the Dynamic Programming method explained in \cite{sutton1998reinforcement}. On the other hand, if the agent does not know the transition function, then he must learn directly values of \textit{state-action} pairs. A very well known model-free method is the classic Q-learning algorithm developed by \cite{watkins1992q}. In either case, model-free or model-based methods, an agent must use information from transitions or from observations. For this reason, Reinforcement Learning uses only associative patterns for finding an optimal policy and this methods can not learn beyond what is expressable by an MDP, which is constrained into associative rules and can not express any other kind of structure, such as causal relations.

@@

The formation and use of causal knowledge in human beings can provide inspiration for our problem, and it has been extensively studied by York Hagmayer and his team. They have found that human beings, while facing a sequential decision problem, use and modify causal information (\cite{hagmayer2008causal}, \cite{hagmayer2009decision}, \cite{hagmayer2010spontaneous}, \cite{hagmayer2013repeated}). In their studies, all of the subjects were faced with a one-stage decision problem in which an initial causal model was provided. In several rounds, the subject made a decision and observed a feedback and was later asked to describe the causal model they thought controlled the situation. The subjects knew that they were supposed to learn a causal model, but the case where the final objective is other than directly learning a causal model has not been studied. \cite{bramley2015conservative} show that people acquire causal structures by selecting the \textit{most informative} options, in the sense of decreasing uncertainty about the true model instead of maximizing expected utility.

@@

In the class of decision problems considered for this proposal it is assumed that the a rational agent must choose some available action and then receive a reward from it. In the case where the agent does not has enough information available, we consider a certain number of learning rounds and expect the agent to output a good action. Problems of this nature have been modelled as \textit{bandit} problems (\cite{sutton1998reinforcement}). A bandit is an analogy of a \textit{slot machine} as the ones found in Las Vegas, where a lever is pulled an some monetary reward (probably cero) is observed. A bandit problem consists by a set of available actions (the arms of the slot machine) and a reward function. It has been shown that the probability of the action selected in the $n$-th round not being optimal has an upper bound (\cite{audibert2010best}), if the optimality criteria is choosen to be the \textit{minimal regret} which is basically the difference of the theoretical mean reward of the optimal action and the chosen action. On the other hand, if the largest mean reward is desired with a fixed confidence of $\delta$, then an algorithm for finding the optimal action exist in such a way that the number of rounds to find it is within a constant factor of a lower bound (\cite{jamieson2014lil}).  If one does not consider a fixed confidence but instead a fixed number of learning rounds (known as fixed budget), then we face a \textit{fixed budget} problem where a lower bound for the probability of finding the optimal arm is given by \cite{carpentier2016tight}. For the case of \textit{unobserved confounders} \cite{bareinboim2015bandits} propose a new metric for bandit algorithms to optimize which achieves better experimental performance.

Notice that none of the previous works consider any kind of causal structure. For this kind of problems, causal relations between actions and consequences could be considered, in this way an action could be conceived as an \textit{intervention} over some environment, which is in fact how humans consider actions in the world (\cite{hagmayer2009decision}); they use and modify causal knowledge during a sequential decision making process (\cite{hagmayer2013repeated}). Consider a set of variables that are causally related between them and to a \textit{reward} variable whose value has to be maximized by intervening one of the variables. It is shown by \cite{lattimoreNIPS2016} that adding causal information in a fixed budget decision problem allows the decision maker to learn \textit{faster} had he not considered causal information. Their work requires that the causal model is fully known to the decision maker, this requirement is relaxed later by \cite{sen2017identifying} who requires only that some part of the causal model is known and allow interventions over the unknown part.

In \cite{lattimoreNIPS2016} a causal graphical model $\mathcal{G}$ is assumed to be known and a number of learning rounds $T$ is fixed. In round $t \in [1,...,T]$ the decision maker chooses $a_t=do(X_t = x_t)$ and observes a reward $Y_t$. After the $T$ learning rounds, the decision maker is expected to choose an optimal action $a^\ast$ that minimizes the \textit{expected regret}, which is defined as $R_T= \mu^\ast - \mathbb{E}[\mu_{a^\ast}]$ where $\mu^\ast = \max \mathbb{E}[a]$. They show that the achieved regret is of a smaller order than the regret obtained by non-causal algorithms. Discovering the causal model itself while using current knowledge to make choices is left as future work in both \cite{lattimoreNIPS2016} and \cite{sen2017identifying}.

Algorithms to discover causal relations in data can be found in \cite{spirtes2000causation}, \cite{eberhardt2008almost}, \cite{hauser2012two}, \cite{hyttinen2013experiment}, \cite{loh2014high}, \cite{shanmugam2015learning} \cite{mooij2016distinguishing}. The most famous of them being the PC-Algorithm (\cite{spirtes2000causation}) which is a constraint-based method for causal discovery, and has an exponential worst-case running time. The PC-Algorithm is based in the Inductive Causation Algorithm proposed in (\cite{judea1990equivalence}). In \cite{hauser2012two} an \textit{active learning} approach to prove a conjecture stated in \cite{eberhardt2008causal} about the worst-case number of experiments required to uniquely discover a causal graph (up to Markov equivalencies)

Also, an \textit{active learning} approach can be used to learn causal models from data, where one starts with some initial graph and then select the instances in the data that allow to add and orient edges in order to end with a fully oriented graph. Active learning algorithms for causal discovery can be found in \cite{tong2001active},\cite{murphy2001active}, \cite{meganck2006learning}, \cite{he2008active}, \cite{hauser2012two}, \cite{10.1007/978-3-319-56970-3_9}, \cite{rubenstein2017probabilistic}.

@@

In this research we are looking for a methodology that will allow to discover causal structure from an uncertain environment while also using it to obtain a reward. Being able to discover the causal structure at the same time that it is being used will allow to eliminate the restriction of knowing the full causal model or part of it. 
\newpage
\section{Methodology}
In this section we describe the steps that are to be followed in order to answer the Hypothesis.
\subsection{A guiding principle for a Causal Decision Problem}
We propose the following principle as a normative guide for how causal information must be used in order to find a solution to a decision problem where the preferences of the decision maker are assumed to be rational. We consider only the case where the decision maker's utility is given by the outcome of a $\{0,1 \}$-binary variable.
\begin{prop}
Let  $\mathcal{G}$ a causal graphical model and let $(\mathcal{A},\mathcal{E},\mathcal{C})$ a decision problem under uncertainty whose actions $a_i = \{ c_j | E_j : j \in J \}$  are causally related to consequences $c \in \mathcal{C}$ through the uncertain events $E \in \mathcal{E}$ which correspond to variables in $\mathcal{G}$. Let $Y$ a variable in $\mathcal{G}$ the variable whose realizations correspond to the consequences of the decision problem once the agent has chosen an action $a \in \mathcal{A}$ and assume that $Y$ only takes values in the set $\{ 0,1\}$ where $1$ is a more desired outcome for the agent. Then, the $\textit{solution}$ for this decision problem is given by the action $a^\ast \in \mathcal{A}$ that satisfies:
\[ P(Y=1 | do(a^\ast) \geq P(Y=1 | do(a)) \textrm{ for all } a \in \mathcal{A}. \]
\end{prop}
\subsection{Modelling a Decision Problem under Uncertainty as a Game}
Consider a decision problem under uncertainty $(\mathcal{A},\mathcal{E},\mathcal{C},\succeq)$ where the available actions $\mathcal{A}$ to a decision maker are causally related to the outcomes $\mathcal{C}$ and this causal relations are captured by a Causal Graphical Model $\mathcal{G}$. The Causal model is assumed to remain fixed and unknown to the decision maker, who is assumed to be rational and aware of the causal nature of the decision problem he faces.

@@

\subsection{Belief Formation}
Once a Game which models the agent-environment interaction is defined, we must turn to the issue about \textit{learning} about the environment, which includes acquiring causal information and also using current causal knowledge in order to obtain new information.

For the agent to learn and reason about the plays of Nature we assume that he is able to observe the final outcome of the game, which includes knowing about the inicial uncertain state that Nature assigned. The agent, at the beginning of the game is uncertain about the state of the environment which he is facing, but he still must take an action, so in order to allow the decision maker to use his knowledge to act, he will have \textit{beliefs} about any relevant aspects of the environment which he will use as if they were the true model in any given play. These beliefs will be \textit{updated} according to what is observed at the end of each move. The second step is to find a way to specify beliefs about causal structure.

@@

The three cases that we notice are:
\begin{enumerate}
\item The decision maker knows the causal model.
\item The decision maker knows only the graphical \textit{structure} of the causal model.
\item The decision maker knows nothing about the causal model. 
\end{enumerate}
In the following we show how the first two cases, which are particular cases of our general problem, can be solved and we show that the proposed solution for the first two cases sheds light on how the general case could be solved.
\subsubsection{Fully knowing the causal graphical model}
If the decision maker knows the causal graphical model, then following the guiding principle, he could easily calculate the effect on the target variable that any of his actions has and then choose the action that has the highest probability of causing a \textit{desired} value of the target variable. The decision thus made is the one that maximizes the expected utility, by construction. Also, choosing this action is the \textit{best response} action, and therefore a Nash equilibrium for the game. Choosing the action that is more likely to produce the most desired outcome according to current causal knowledge is required by Joyce's Causal Decision Theory (\cite{joyce1999foundations}).
\subsubsection{Knowing only the graph structure}
If a decision maker knows the structure of the graph, but he does not know the parameters, then he encodes this ignorance, along with any useful previous knowledge, as a probability distribution over a suitable space. In the preliminary results, which will be shown later, a particular case is considered, where the beliefs have the form of a Dirichlet distribution for each of the Conditional Probability Tables that characterize a Bayesian Network.

In general, what must be specified is a way of encoding current causal knowledge into a probability distribution in such a way that a \textit{local} (i.e. in each round) causal model can be obtained from current beliefs in order to make a decision using current causal knowledge and those beliefs will be later updated using what is observed after choosing an action.  The action will be chosen, given a set of beliefs, as in the previous case and by following the guiding principle. This means that using current beliefs, the agent forms a causal model which is used as if it were the true causal model.
\subsubsection{General case: Model unknown}
The previous two cases are per se steps of the methodology, rather simplifications in order to understand what is happening. The real deal is the case where the causal model is unknown. When the causal model is unknown, two cases of interest appear, depending if the decision maker knows the (maximum) number of variables in the model or not.

@@

Given a number $T$ of rounds, and in round $t \in \{1,2,...,T \}$ the agent will make an action $a \in \mathcal{A}$ and then observe the state of the other variables of the model. Using this information, current beliefs will be updated according to the criteria to be established.

@@

\end{itemize}
\subsubsection{Publications plan}
\begin{itemize}
\item \textbf{Year 1:} Gonzalez-Soto, M., Sucar, L.E., Escalante, H.J., \textbf{Playing against Nature: causal discovery for decision making under uncertainty}. Accepted for poster presentation at the \textbf{CausalML 2018 Workshop at ICML 2018}. July 15 2018, Stockholm, Sweden. This can be confirmed at \url{https://sites.google.com/site/faim18wscausalml/program-schedule}. The paper can be found at \url{https://arxiv.org/abs/1807.01268}.
\item \textbf{Year 2:} Conference Paper
		\begin{itemize}
		\item The implications of Causal Relations for Decision Making: a general principle for Decision under Uncertainty.
		\item Possible Forum: Conference on Uncertainty in Artificial Intelligence (UAI), International Conference Machine Learning (ICML)
		\end{itemize}
\item \textbf{Year 2:} Conference Paper
	\begin{itemize}
	\item When a causal model is unknown, how to encode uncertainties about causal structure in a probabilistic distribution? Bayesian Nonparametric prior that explicitly represents causal structure.
	\item Possible Forum: International Conference on Bayesian Nonparametrics, International Conference on Probabilistic Graphical Models.
	\end{itemize}
\item \textbf{Year 3:} Journal Paper
		\begin{itemize}
			\item Aim: Theoretical paper of results for on-line causal learning.
		\end{itemize}
\end{itemize}

@@

\[ f(x_1,...,x_k | \alpha_i,...,\alpha_k)=\frac{1}{B(\alpha)}  \prod_{i=1}^k x_i^{\alpha_i-1}\]

@@

\subsubsection{Implementation}
We begin with a random assignment of the $\alpha$ parameter for each of the distributions considered. We use Dirichlet distribution for each of the conditional probability tables that appear in the factorization of the joint probability for the graph of $\mathcal{G}$. Since each of the variables in the model is binary, then the product of these Dirichlets is Dirichlet.

@@

The average performance over $20, 50, 100$ and $200$ rounds is shown in Figure 2 - 5.
